\chapter{Introduction}
\label{c:intro}

\section{Machine-to-machine}
M2M application is about utilizing a set of connected devices to achieve a predefined goal. M2M application?s has its capability to monitor, control and manage remote assets. You can deploy several sensors to sense environmental condition. You can also deploy several sensors and actuators to perform a specific action to make environment better. You can further control the logical part of these connected device namely, remote assets, to make them reconfigurable.

\section{M2M application development}
Generally speaking, M2M application development can be divided into three phases.

\section{WuKong: Intelligent M2M middleware}
WuKong is an intelligent M2M middleware for service-oriented M2M systems, has set up the goal to allow programmers develop M2M applications with ease by introducing a new programming paradigm called flow-based programming (FBP) to offer drag-and-drop software components and flow-chart like programs with automatic sensor identification, sensor mapping, node configuration, system-reconfiguration. A FBP represents all the relations between logical components which is also called as the 

\section{Sensor Mapping}
Sensor mapping is important. For an application to be deployed to thousands of households, it will be very costly for a M2M application developer to customize FBP for every household. For example, choosing usable temperature sensors in one room. Developer has no idea about how many sensors are there in every house?s room. Therefore, sensor mapping plays an important role since it can realize developer?s desired functionality into target environment.


\section{M2M/IoT application}
What is M2M/IoT application?

M2M application is about utilizing a set of connected devices to achieve a predefined goal. M2M application’s has its capability to monitor, control and manage remote assets. You can deploy several sensors to sense environmental condition. You can also deploy several sensors and actuators to perform a specific action to make environment better. You can further control the logical part of these connected device namely, remote assets, to make them reconfigurable.

\section{Challenges}

\section{Thesis Objectives}

\section{Thesis Organization}
blah blah blah 



