\chapter{Problem Description}
\label{c:prob_desc}


% IoT's challenge 
\section{Problem Definition}
We want to make programming IoT much more painless by providing IoT middleware support. WuKong is the middleware that supports IoT programmer to program IoT applications as a system instead of node by node programming. A programmer can utilize flow-based programming tools to design their IoT applications which contain sensing units, actuating units and data processing units without caring the target environment limitation. By interacting with programming user interface, programmer can utilize drag-and-drop tools and a set of loose coupling components to program their IoT programs in visual way. The programmer?s duty is to design the logical side of IoT application, WuKong middleware will then perform service discovery, service search, service selection, service composition and map the each component in application?s logical side to their physical environment in optimized way. For example, if there is a component named ?Temperature?, the WuKong will map this ?Temperature? to a set of the most appropriate temperature sensors based on user requirement on this component. 

Each IoT application can be recognized as a service in WuKong middleware, and service can consist of a set of basic service such as light sensor, humidity sensor, PIR sensor. The component that programmer is dragging can be seen as a service. Finding the best set of device to fulfill the component/service is my best interest. There are two problems before we can do service mapping. 

First is that we need to be able to profile every communicating units such(Accuracy, Availability, Battery life time ? ) in IoT, otherwise we cannot get the information from sensors, actuators, computing units. How to profile sensor description is also a challenge in IoT, we need to take care about interoperability. 

The second is that as a role of programming tool, we have to take care about the way we acquire user requirement from IoT programmers. Ask them to specify very detailed description may not be feasible since the IoT programmers might not be an expert in the field of Wireless Sensor and Actuator Network(WSAN). Providing an easy-to-use tools to acquire user requirement is also a problems to design such a middleware support for IoT programmers.

\section{Service-oriented middleware support for IoT}

IoT programmers would like to design their programs by hundreds of thousands devices in IoT world. To deal with Interoperability and scalability in IoT when programmers want to develop an IoT program, middleware support is needed for IoT programmer to program IoT program. 
%what kind of middleware support can WuKong provide

With middleware support, programmer can utilize graphical user interface to program their IoT application
\section{Mapping between logical and physical side of a M2M application}

% middleware support 

In order to support IoT programmer to focus on programming the logical side of M2M application. The mapping process between the logical and physical side is very important. 

Sensor mapping is important. For an application to be deployed to thousands of households, it will be very costly for a M2M application developer to customize FBP for every household. For example, choosing usable temperature sensors in one room. Developer has no idea about how many sensors are there in every house’s room. Therefore, sensor mapping plays an important role since it can realize developer’s desired functionality into target environment.



